dendro

### 2017-05-25 analysis/test-bai.Rmd
update chron

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

@@

w <- summary(bai_sj)
mean(w$year)
mean(w$stdev)

plot(bai_sj, plot.type="spag")

cro_sjb <- chron(bai_sj, prefix = "SJ", biweight = TRUE)
 plot(cro_sjb, add.spline=TRUE, nyrs=30)

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

```{r}
# Robust mean biweith or not
cro_sjb <- chron(bai_sj, prefix = "SJ", biweight = TRUE)
cro_sjnotb <- chron(bai_sj, prefix = "SJ", biweight = FALSE)

cro_b <- cro_sjb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

cro_notb <- cro_sjnotb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

# Compute chronologies of BAI

chrono_bai <- function(bai_data, prefix){

    if (length(prefix) == 0) {
        prefix.str <- ""
    }
    else {
        prefix.str <- as.character(prefix)[1]
        if (is.na(prefix.str) || Encoding(prefix.str) == "bytes" || 
            nchar(prefix.str) > 3) {
            stop("'prefix' must be a character string with less than 4 characters")
        }
    }
    n_trees <- rowSums(!is.na(bai_data))

    out <- bai_data

    out <- data.frame(samps)
    out
}

### Compute Chrono

b <- bai_sj

chrono_bai <- function(bai_object, alpha){ 
  require(dplyr)

  b <- bai_object 
  alpha <- as.numeric(alpha)

  # Prepare data 
  b_aux <- b %>% 
  ##  Create a variable of year 
  mutate(year = as.numeric(rownames(.))) %>% 
  ## melt data 
  gather(series, bai, -year) %>% 
  # remove NA values 
  filter(bai != "")

  # Compute mean, sd, se and sample deepth (n_trees)
  out <- b_aux %>% 
  group_by(year) %>% 
  summarise(bai_mean = mean(bai), 
            bai_sd = sd(bai), 
            bai_se = bai_sd / sqrt(n()), 
            n_trees = n()) %>% 
  as.data.frame()

  # Loess 
  l <- loess(b_aux$bai ~ b_aux$year, span = alpha)
  years_v <- seq(min(b_aux$year), max(b_aux$year), 1)

  l_pred_aux <- predict(l, years_v, se=TRUE)
  l_pred <- as.data.frame(cbind(loess_fit = l_pred_aux$fit, 
                loess_se = l_pred_aux$se.fit,
                year = years_v))

  out <- out %>% inner_join(l_pred, by='year')

  out
}

c_sj <- chrono_bai(bai_sj, alpha=0.75)

c_sj

c_sj %>% ggplot(aes(x=year, y=bai_mean)) + 
  theme_bw() + 
  geom_ribbon(aes(x= year, 
                  ymin = loess_fit - 1.96*loess_se,
                  ymax = loess_fit + 1.96*loess_se), na.rm = FALSE, 
              fill = "grey") +
  geom_line() + geom_point() + 
  geom_line() + geom_smooth(method= 'loess', span = 0.75, se=FALSE)

bb2 %>% ggplot(aes(x=year, y=bai_mean)) + 
  theme_bw() + 
  geom_ribbon(aes(x= year, 
                  ymin = bai_mean - bai_se,
                  ymax = bai_mean + bai_se), na.rm = FALSE, 
              fill = "grey") +
  geom_line() + geom_point() + 
  geom_smooth(method= 'loess', span = 0.30, se=FALSE)

# IC LOESS

  geom_smooth(method= 'loess', span = 0.30, se=FALSE) + theme_bw() + 
  geom_bar(aes(x=year, stat = (samp.depth*10), colour=treatment))

# cc <- chrono_bai(bai_sj, prefix = "SJ")

@@

# SJ

cro_sj <- chron(bai_sj, prefix = "SJ", biweight = TRUE)
cro_sj %>% plot(add.spline=TRUE, nyrs=30)

cro_ca <- chron(bai_ca, prefix = "CA", biweight = TRUE)
cro_ca %>% plot(add.spline=TRUE, nyrs=30)

cro_ca2 <- cro_ca %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('CA')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

cro_sj2 <- cro_sj %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('SJ')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

cro2 <- rbind(cro_ca2, cro_sj2)

cro2 %>% ggplot(aes(x=year, y=bai_mean, colour=treatment)) + 
  geom_line() + geom_smooth(method= 'loess', span = 0.30, se=FALSE) + theme_bw() + 
  geom_bar(aes(x=year, stat = (samp.depth*10), colour=treatment))

  geom_point(aes(x=year, y = samp.depth*100))

cro_ca2 %>% ggplot(aes(x=year, y=bai_mean)) + 
  geom_line(colour='gray') + geom_smooth(method= 'loess', span = 0.80, se=FALSE) + theme_bw() 
+
  geom

plot()

str(cro_ca)

names(cro_ca)

cro_ca <- chron(bai_ca, prefix = "CA", biweight = TRUE)
plot(cro_sjb, add.spline=TRUE, nyrs=30)
